---
title: "DataImportAndCleaning"
author: "Dan Murphy"
date: "August 16, 2016"
output: github_document
---

The normalized data was exported from [NYSDrillTeams](http://www.nysdrillteams.com).  The code below loads the CSV files, updates certain column names in order to complete the joins, and executes the joins.   

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(lubridate)
```

```{r, eval=FALSE}
df  <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_events_results.csv")
df2 <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_teams.csv")
df3 <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_eventtypes.csv")
df4 <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_drills.csv")
df5 <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_seasons_drills.csv")
df6 <- read.csv("C:/Users/murph/Desktop/R/2016FDRacingPrediction/RawData/nysdt_seasons_events.csv")

colnames(df2)[1] <- "team_id"
colnames(df6)[1] <- "event_id"
colnames(df5)[1] <- "seasondrill_id"
colnames(df3)[1] <- "type"
colnames(df4)[1] <- "drill_id"

df <- left_join(df, df2, by = "team_id")
df <- left_join(df, df6, by = "event_id")
df <- left_join(df, df5, by = "seasondrill_id")
df <- left_join(df, df3, by = "type")
df <- left_join(df, df4, by = "drill_id")

remove(df2,df3,df4,df5,df6)
```

The dataframe is next trimmed to omit extraneous columns  Then, names and data types are corrected.  Last, the dataset is filtered to only include runs from motorized teams in 2016. 

```{r, eval=FALSE}
AllData <- data.frame(df$id, df$team_name, df$name.x, df$name.y, df$start_date.y, df$rank,df$performance,    
                  df$division)
colnames(AllData) <- c("WebsiteID","Team","TimeContest","TournName","TournDate","Rank","Time","Division")

AllData$TournDate <- mdy_hm(AllData$TournDate)
AllData$Time <- as.numeric(levels(AllData$Time))[AllData$Time]

AllData <- AllData %>% filter((Division %in% c("Exhbition","Motorized")) & (TournDate > ymd("2016/01/01"))) 
AllData <- AllData %>% filter((TournName != "Nassau County Old-Fashioned") & 
                      (TournName != "Long Island Championship (OF)") & 
                      (TournName != "New York State Old Fashioned Drill")& 
                      (TournName != "Mike Esposito Memorial Drill"))
AllData <- AllData %>% filter((TimeContest != " *********** LINEUP ***********") & 
                      (TimeContest != "B Hose - CANCELED (RAIN)") & 
                      (TimeContest != "Individual Ladder - SCHEDULED"))

AllData <- separate(AllData, TimeContest, c("TimeContest","discard"), sep = " - ")
AllData$discard <- NULL

AllData <- AllData %>% filter((TimeContest != "Individual Ladder")& 
                              (TimeContest != "Motor Hose Replacement")& 
                              (TimeContest != "Combination Hose & Pump")& 
                              (TimeContest != "Efficiency Replacement")& 
                              (TimeContest != "Two into One"))

AllData$TimeContest <- ifelse(AllData$TimeContest=="3 Man Ladder","Three Man Ladder",AllData$TimeContest)

```

From the summary statistics gathered in StateSimParams, results are next simulated and then again another summary is taken.  



